---
title: "useR! 2019 Recap"
author: "Ezgi Karaesmen & Katie Sasso-Schafer"
date: "`r format(Sys.time(), '%a %b %d %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message=FALSE)
#devtools::install_github("tidyverse/tidyr")
#devtools::install_github("chrk623/dataAnim")
```


## Session: Reproducibility

### Package flextable: a grammar to produce tabular reporting from R - Quentin Fazilleau

See details [davidgohel.github.io/flextable/articles/format.html](https://davidgohel.github.io/flextable/articles/format.html)

```{r}
library(flextable)
library(tidyverse)
library(tidyr)
library(usethis)

ft <- flextable(head(mtcars))
ft <- color(ft, i = ~ drat > 3, j = ~ vs + am, color = "red")
ft <- bg(ft, i = ~ wt < 3, j = ~ mpg, bg = "#EFEF99")
ft <- bold(ft, i = 2:4, j = "cyl", bold = TRUE)
ft
```

### Connecting R/R Markdown and Microsoft Word using StatTag for Collaborative Reproducibility - Leah Welty

<iframe width="560" height="315" src="https://www.youtube.com/embed/K3QwG4LB9a4" frameborder="0" allowfullscreen></iframe>


To download and get more details on how to use it go to https://sites.northwestern.edu/stattag/

### `auth0`

authanticate shiny access ?

### ggwordcloud

https://github.com/lepennec/ggwordcloud

### tidyr::pivot_longer!

Enhancements to data tidying  - Hadley

New versions of gather and spread!

- Two key tidyr functions for solving
  + pivot_longer (previously gather) columns
  + pivot_wider  (previously spread)
- Available on github for now

Animations to show what they do  in dataAnim

```{r }
#devtools::install_github("tidyverse/tidyr")
#devtools::install_github("chrk623/dataAnim")
library(dataAnim)
gather_anim(
   key = "Subject",
   value = "Score",
   col = c("English", "Maths"),
   data = datoy_wide
 )
```


```{r}

#pivot_longer
datoy_wide %>% 
  pivot_longer(cols = English:Maths, names_to = 'Subject',
             values_to = "Score")
  
  
#pivot_wider

datoy_long %>% 
  pivot_wider(names_from = Subject, values_from = Score)

```

Untangling list column 
```{r}
?unnest_auto
?unnest_longer
?unnest_wider
```

<iframe width="700" height="315" src="https://tidyr.tidyverse.org/dev/articles/pivot.html" frameborder="0" allowfullscreen></iframe>


### n() cool #dplyr things -- Romain

[slides](https://speakerdeck.com/romainfrancois/n-cool-number-dplyr-things)

Group function updates
```{r}
?group_modify
?group_split
```


Column wise

- Replace group_by and summarise. Action and selection at the same time is what you do with group_by and summarise
- Which summarise_at we can separate concept of selection and function 
    + Less error prone. Only have to change the function in one place 
    + Can do this with your own function 

```{r}
iris %>% 
  group_by(Species) %>% 
  summarise_at(
    vars(contains("Petal"), contains("Sepal")),
         mean)

```

### DRY out your workflow with the usethis package

Jenny Bryan

Workflow functions directly to be called 
```{r}
?create_package()
?create_project()
```

use_this demo videos

```{r}
?use_github()
?use_mit_license()

```

good functions for workshops and teaching 

```{r}
?usethis::use_course()
?usethis::use_zip()
```

### Reusing tidyverse code, the easy way 
Lionel Henry

Tidy Eval 

- Powers data masking from the rlang package 
- Flexible and robust 
- "`r {{2 + 2}}`" replacing !! and enquo

- Need latest version of rlang

<iframe width="700" height="315" src="https://tidyeval.tidyverse.org/" frameborder="0" allowfullscreen></iframe>

[slides here](https://speakerdeck.com/lionelhenry/reusing-tidyverse-code)


### mlr3

Nice alternative to Caret

Github

<iframe width="700" height="315" src="https://github.com/mlr-org/mlr3" frameborder="0" allowfullscreen></iframe>

Book (work in progress)

<iframe width="700" height="315" src="https://mlr3book.mlr-org.com/use-cases.html" frameborder="0" allowfullscreen></iframe>


### FREE shiny app authentication 

autho0 Package


<iframe width="700" height="315" src="https://github.com/curso-r/auth0" frameborder="0" allowfullscreen></iframe>




